%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {D-Soft. JSC} % Organization
    {Da Nang, Viet Nam} % Location
    {Mar. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I'm in charge of building and maintaning two projects.}
        \item {The first project is an application to handle process of unloading fuel on Tank Truck to Underground Tank of Gas Station}
          \begin{itemize}
            \item {Implemented Bluetooth to control and navigate hardware on Truck and Gas Station.}
            \item {Integrated iBeacon for detecting distance between iOS application and Tank Truck or Gas Station to restrict using outside specified area.}
          \end{itemize}
        \item {The second one is a Chat/Call system}
          \begin{itemize}
            \item {It has 4 main functions which private messaging, group chat, audio/video call, audio/video group call.}
            \item {Built an iOS application with Swift.}
            \item {Built back-end using Node.js.}
            \item {Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS EC2.}
            \item {Integrated Rocket.Chat open source.}
            \item {Integrated WebRTC open source.}
          \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Freelance} % Organization
    {Da Nang, Viet Nam} % Location
    {Oct. 2018 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was asked to update an existing iOS apps to the latest version of iOS and to fix any issues caused by this as well as a few other existing issues.}
        \item {This projects had a very tight time scale and I was able to complete it in very good time while providing regular updates to the client.}
        \item {In that time, I had to handle and build a few projects from zero like a Project Manager.}
        \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, IAM).}
        \item {I also learnt some new tech skills related to Back-end, Machine Learning, Data Science, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iOS Developer} % Job title
    {Asian Tech Co., Ltd.} % Organization
    {Da Nang, Viet Nam} % Location
    {Jun. 2015 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {At my fifth year at University, I decided to work full-time at Asian Tech.}
        \item {During my time at Asian Tech I was able to work on a large number of projects.}
        \item {I enjoy being able to work with clients to understand and surpass their expectations.}
        \item {At Asian Tech I was also given the oppertunity to work with all of my core skills and to gain new skills in things such as Java.}
        \item {Some of skills that I learnt at here:}
          \begin{itemize}
            \item Designed, developed and distributed iOS applications.
            \item Implemented MVC and MVVM structure for project.
            \item Implemented Rxswift
            \item Built and integrated RESTful API.
            \item Integrated CI/CD with TravisCI, CircelCI and Fastlane.
            \item Implemented and built a Server-side using Vapor framework.
            \item Researched and wrote Reactive Programming, RxSwift documents.
            \item Implemented Unit testing, using Quick, Nimble and RxTest.
            \item Implemented Functional Programming.
            \item Built and deploy services using Nginx, AWS services (EC2, S3, RDS) and Google Clouds.
            \item Used Github, Gitlab and Bitbucket for project repository.
            \item Team leader - Code reviewer as a code member of iOS team, mentor of junior members and interns.
            \item Sharing technical knowledge through Workshop, Presentation.
            \item Designed, developed and distributed iOS applications.
            \item Implemented and built a Face Recognition System in ML field using TuriCreate, Vision and CoreML frameworks.
          \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fresher - Bootcamp} % Job title
    {Enclave} % Organization
    {Da Nang, Viet Nam} % Location
    {Jan. 2015 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I started working for Enclave company full-time during my fourth year at University.}
        \item {It was during this role that I learnt many of the fundamentals that I have been building on over the past 3 years.}
        \item {I feel like having the opportunity to use a large range of different things early on in my career has given me the drive to always want to try new tools and frameworks.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
